\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/ex.tex
color
minor

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output.

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby}\footnote{This is also how a program written directly in
  ABY would look like.}. shows the output code for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation

@@

\begin{figure}
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\text{{\color{red}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$

$\mathtt{
for(uint32\_t\;i\;=\;0;\;i\;<\;30;\;i = i + 1)\;\{\;\;\text{\color{red}//acc = w}^{\text{{\color{red}T}}}\text{\color{red}x}~\label{line:dotproductloop}
}$
$\mathtt{
\;\;\;\;share\;*a\_t\_0 = acirc\rightarrow PutMULGate(a\_w[i], a\_x[i]);~\label{line:dotmulgate}
}$
$\mathtt{
\;\;\;\;a\_acc = acirc\rightarrow PutADDGate(a\_acc, a\_t\_0 );~\label{line:dotaddgate}
}$
$\mathtt{
\}
}$

@@

$\mathtt{
if(role == CLIENT) \{\;\;\text{\color{red}//only to the client}
}$
$\mathtt{
\;\;\;\;uint32\_t \_o = y\_out\rightarrow get\_clear\_value\langle uint32\_t \rangle();
}$
$\mathtt{
\}
}$
\end{lstlisting}
\caption{\tool compiler (partial) output for Figure~\ref{fig:ex-sml}}
\label{fig:ex-aby}
\end{figure}

\subsubsection*{Circuit generation and evaluation} The next step in
\tool is to
compile the output C++ code and execute it. Doing so evaluates away the
public parts of the program, including the array accesses, and
generates a \mpc circuit comprising of arithmetic and boolean gates,
with appropriate conversion gates. The circuit is then evaluated using
a \mpc protocol.

>>>>

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation

@@

\begin{figure}
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\textbf{{\color{blue}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$

$\mathtt{
for(uint32\_t\;i\;=\;0;\;i\;<\;30;\;i = i + 1)\;\{\;\;\textbf{\color{blue}//acc = w}^{\textbf{{\color{blue}T}}}\textbf{\color{blue}x}~\label{line:dotproductloop}
}$
$\mathtt{
\;\;\;\;share\;*a\_t\_0 = acirc\rightarrow PutMULGate(a\_w[i], a\_x[i]);~\label{line:dotmulgate}
}$
$\mathtt{
\;\;\;\;a\_acc = acirc\rightarrow PutADDGate(a\_acc, a\_t\_0 );~\label{line:dotaddgate}
}$
$\mathtt{
\}
}$

@@

$\mathtt{
if(role == CLIENT) \{\;\;\textbf{\color{blue}//only to the client}
}$
$\mathtt{
\;\;\;\;uint32\_t \_o = y\_out\rightarrow get\_clear\_value\langle uint32\_t \rangle();
}$
$\mathtt{
\}
}$
\end{lstlisting}
\caption{\tool compiler (partial) output for Figure~\ref{fig:ex-sml}}
\label{fig:ex-aby}
\end{figure}

\subsubsection*{Circuit generation and evaluation} The next step in
\tool is to
compile the output C++ code and execute it. Doing so evaluates away the
public parts of the program, including the array accesses, and
generates a  circuit comprising of arithmetic and boolean gates,
with appropriate conversion gates. The circuit is then evaluated using
a \mpc protocol.

### 2017-10-31 OaklandSubmission/intro.tex
color
minor

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and therefore cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a, general
 purpose, high-level programming language and a
 tool, e.g., a compiler would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

@@

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w$ and $x$. Alice has following options.

@@

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;w[30] = input1();\;\;uint\;b = input1();
}$
$\mathtt{
uint\;x[30] = input2();
}$
$\mathtt{
uint\;acc = 0;
}$
$\mathtt{
for\;i\;in\;[0:30]\;\{\;acc\;=\;acc\;+\;(w[i]\;\times\;x[i]);\;\}
}$
$\mathtt{
output2((acc > b)\;?\;1\;:\;0)\;\text{{\color{red}//only to party 2}}
}$
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}

@@

\subsubsection*{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs. As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme, against semi-honest (or, ``honest but curious") adversaries,
 to the security of the  \mpc back-end. 
 We also prove a formal security theorem against semi-honest  adversaries for our partitioning
scheme (Section~\ref{sec:ld} and Section~\ref{sec:pipe}).

\subsubsection*{Evaluation} We have implemented \tool
using ABY~\cite{aby} as the
cryptographic back-end. We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also the matrix factorization example
from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of the \bonsai~\cite{bonsai} classifier, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x) their state-of-the-art, hand-crafted implementations. Finally, we
demonstrate the usefulness of partitioning by implementing an application
that requires more than 300 million gates (Section~\ref{sec:impl} and
Section~\ref{sec:eval}).

>>>>

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a, general
 purpose, high-level programming language and a
 tool, e.g., a compiler would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

@@

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Suppose Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w$ and $x$. Alice has following options.

@@

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;w[30] = input1();\;\;uint\;b = input1();
}$
$\mathtt{
uint\;x[30] = input2();
}$
$\mathtt{
uint\;acc = 0;
}$
$\mathtt{
for\;i\;in\;[0:30]\;\{\;acc\;=\;acc\;+\;(w[i]\;\times\;x[i]);\;\}
}$
$\mathtt{
output2((acc > b)\;?\;1\;:\;0)\;\textbf{{\color{blue}//only to party 2}}
}$
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}

@@

\subsubsection*{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or, ``honest but curious") adversaries
 to the semi honest security of the  \mpc back-end. 
 We also prove a formal security theorem against semi-honest  adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).

\subsubsection*{Evaluation} We have implemented \tool
using ABY~\cite{aby} as the
cryptographic back-end. We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also the matrix factorization example
from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of the \bonsai~\cite{bonsai} classifier, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x) their state-of-the-art, hand-crafted implementations. Finally, we
demonstrate the usefulness of partitioning by implementing an application
that requires more than 300 million gates (\sectionref{impl} and~\sectionref{eval}).
